\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault,light]{FiraSans}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\geometry{
  left=1in,
  right=1in,
  top=1in,
  bottom=1in
}

\definecolor{links}{HTML}{1565C0}
\hypersetup{
  colorlinks=true,
  urlcolor=links,
}

% Left-align signature
\longindentation=0pt

\signature{John Doe}
\address{123 Main Street\\San Francisco, CA 94102\\john.doe@email.com\\+1 555 123 4567}

\begin{document}

\begin{letter}{Hiring Manager\\Company Name\\456 Business Ave\\City, State 12345}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Software Engineer position at your company. With over seven years of experience building scalable web applications and distributed systems, I am excited about the opportunity to contribute to your team.

In my current role as Senior Software Engineer at Acme Tech Inc., I have led the development of microservices architecture serving over 2 million daily users. I have a proven track record of reducing API response times by 40\% through strategic caching and query optimization, and I have mentored a team of four junior developers through code reviews and pair programming sessions.

My technical expertise spans both backend and frontend development. I am proficient in Go, Python, and TypeScript, and have extensive experience with cloud infrastructure on AWS. I am particularly passionate about system design, clean code practices, and building engineering teams that deliver high-quality software.

I am drawn to your company's mission and the technical challenges you are solving. I believe my experience in building scalable systems and leading technical initiatives would make me a valuable addition to your team.

Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experience align with your needs. I am available for an interview at your convenience.

\closing{Sincerely,}

\end{letter}

\end{document}
